Carbonate chemistry at Ny-Ålesund

### 2021-11-15 awipev-CO2.Rmd
extensive revision of ggreg applied to pCO2 measured vs calculated

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y") { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
#reg <- fit$regression.results[ty,] #one selects OLS only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = paste(title, "; type: ", type,
                     "\n R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3)),
       subtitle = subtitle,
       x = xlab,
       y = ylab)
  return(plt)
  } #else {
  #return(fit)
#}
}

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
title <- "pCO2 normalized at in situ temperature"
fit <- lmodel2(data = d_all,   pco2_calc_fb_insi_temp ~ pco2_fb_insi_temp, nperm = 99)
print(fit)
p <-  ggplot(d_all,aes(x = pco2_fb, y = pco2_calc_fb))+
  geom_point()+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  # labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
  #                    "; Intercept =", signif(fit$regression.results[2,2], 3),
  #                    "; Slope =", signif( fit$regression.results[2,3], 3),
  #                    "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1, xlim=c(200,420), ylim=c(200,420))+
  labs(title = "", x="Measured pCO2", y="Calculated pCO2") + theme_bw()  
print(p)
ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
```

>>>>

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y", proplot = TRUE) 
  { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
#reg <- fit$regression.results[ty,] #one selects OLS only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
error <- xdata - predicted
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = paste(title, 
                     "\ntype: ", type,
                     "; R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "\nP =", signif(fit$P.param, 3),
                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
       subtitle = subtitle,
       x = xlab,
       y = ylab) +
    theme_bw() +
    theme(plot.title = element_text(size = 7))
    if (proplot == TRUE) { # property-property plot
      plt <- plt +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        theme(aspect.ratio = 1)
      }
  return(plt)
  } #else {
  #return(fit)
#}
}

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
title <- "pCO2 normalized at in situ temperature"
p <- ggreg(
  xdata = d_all$pco2_fb_insi_temp,
  ydata = d_all$pco2_calc_fb_insi_temp,
  type = "MA",
  plot = TRUE,
  title = title,
  subtitle = "",
  xlab = "Measured pCO2",
  ylab = "Calculated pCO2",
  proplot = TRUE
)
print(p)
ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
```
